\cvsection{Experience}
\begin{cventries}
	\cventry
	{Team Lead, Flight Software}
	{\href{http://www.teamindus.in/}{Team Indus (Axiom Research Labs Pvt. Ltd.)}}
	{Bangalore, India}
	{May. 2015 - Present}
	{
		\begin{cvitems}
			\item{Leading a team of seven people in developing software systems for \textbf{orbital} and \textbf{descent} phases of lunar mission, with onboard state estimation, autonomous attitude correction, lunar terrain feature tracking, and limited fault detection, isolation, and recovery.}
			\item{Developed frameworks for continuous integration, multi-platform compiling and testing, generation of new tests, and \textbf{Processor in Loop Simulation (PiLS)}. Conducted regular PiLS exercises of various phases of the mission.}
			\item{Developed software systems to verify lunar descent strategy, support functional and environmental tests of lander navigation sensors and rover mast, and support structural tests of lunar rover engineering model on lunar simulant test bed.}
		\end{cvitems}
	}

	\cventry
	{Intern, \href{http://www.ti.com/corp/docs/innovation/research-development/Kilby-Labs.html}{Kilby Labs}}
	{\href{http://www.ti.com/}{Texas Instruments}}
	{Bangalore, India}
	{May. 2013 - Jul. 2013}
	{
		\begin{cvitems}
		\item{Gained exposure to chip development process for a multi signal processsor (MSP 430), as part of a larger team. The goal of the project was to reduce the power consumption by an order of magnitude, compared to the nominal design. Performed Statistical Timing Analysis on critical paths in new design, with Monte Carlo simulations of paths in HSPICE.}
		\item{Developed framework to collate timing-critical paths under a known set of operating conditions, and simulate the same paths under various operating conditions to determine behavioral trends.}
		\end{cvitems}
	}

	\cventry
	{Teaching Assistant, Advanced Communication Lab}
	{Indian Institute of Technology Madras}
	{Chennai, India}
	{Aug. 2014 - Nov. 2014}
	{
		\begin{cvitems}
		\item{Practical course with \href{http://www.ee.iitm.ac.in/~andrew/}{Prof. Andrew Thangaraj}, dealing with PHY layer implementation in communication systems.}
		\item{Students implemented Digital Radio Mondiale (DRM) receivers with RTL-SDR dongles.}
		\end{cvitems}
	}

\end{cventries}
