\cvsection{Extra-Curricular Activities}
\begin{cventries}
	\cventry
	{Core Member, Web and Mobile Operations.}
	{Saarang 2013}
	{Chennai, India}
	{May. 2012 - Jan. 2013}
	{
		\begin{cvitems}
		\item{Part of 24-member core team responsible for organizing Saarang 2013, the student run cultural festival of IITM.}
		\item{Led a team of 17 students developing and deploying web and mobile services to support organizers and participants, numbering over 50,000.}
		\end{cvitems}
	}

	\cventry
	{Literary Affairs Secretary, Tapti Hostel}
	{LitSoc 2012-2013}
	{Chennai, India}
	{Aug. 2012 - May. 2013}
	{
		\begin{cvitems}
		\item{Organized hostel's participation in LitSoc events, including creative writing, mono-acting, treasure hunts, etc.}
		\item{Placed 4th out of 18 hostels overall.}
		\end{cvitems}
	}

	\cventry
	{Coordinator, Web Operations}
	{Saarang 2012}
	{Chennai, India}
	{May. 2012 - Jan. 2013}
	{
		\begin{cvitems}
		\item{Part of 3-member team responsible for developing sales portal for ticket sales to Saarang's professional shows, for 9000-strong population of IITM.}
		\end{cvitems}
	}

	\cventry
	{}
	{Carnatic Music}
	{}
	{Oct. 2002 - Present}
	{
		\begin{cvitems}
		\item{Flautist, studying Carnatic Music since 2002. Passed junior exam in 2003. Performed at multiple musical events in Bangalore.}
		\end{cvitems}
	}

	\cventry
	{}
	{Trekking}
	{}
	{}
	{
		\begin{cvitems}
		\item{Trekked across Chanderkhani pass (Himalayas), as well as several places in Karnataka, India.}
		\end{cvitems}
	}

	\cventry
	{}
	{Reading}
	{}
	{}
	{
		\begin{cvitems}
		\item{Vociferous reader.}
		\end{cvitems}
	}

\end{cventries}
