\cvsection{Industry Experience}
\begin{cventries}
	\cventry
	{Team Lead, Flight Software}
	{Team Indus (Axiom Research Labs Pvt. Ltd.)}
	{Bangalore, India}
	{May. 2015 - Present}
	{
		\begin{cvitems}
			\item{Leading a team of seven people developing software for the lunar lander.}
			\item{Developed software system for \textbf{orbital phase of lunar mission}, capable of onboard state estimation, autonomous attitude correction, man-in-loop orbital maneuvers, and limited fault detection, isolation, and recovery.}
			\item{Developed software system to perform an \textbf{autonomous lunar descent sequence}, with onboard estimation of lander states, constrained landing site selection, and targeted descent to selected landing site.}
			\item{Developed software system to verify lunar descent strategy, using flight grade descent sensors mounted on hexacopter and flown across representative terrain in pre-defined patterns.}
			\item{Developed framework for functional and environmental tests of lander navigation sensors, and in-house designed rover mast.}
			\item{Developed framework for structural tests of lunar rover engineering model on test bed of lunar simulant.}
			\item{Developed framework for continuous integration, multi-platform compilation and testing, and easy generation of new unit and integration level tests with existing CUnit and PyUnit libraries.}
			\item{Developed framework for \textbf{Processor in Loop Simulation (PiLS)} system emulating sensor and actuator electrical interfaces to lander avionics unit.}
			\item{Responsible for regular comprehensive PiLS exercises of lunar lander avionics system.}
		\end{cvitems}
	}

	\cventry
	{Intern, Kilby Labs}
	{Texas Instruments}
	{Bangalore, India}
	{May. 2013 - Jul. 2013}
	{
		\begin{cvitems}
		\item{Gained exposure to chip development process for a multi signal processsor, as part of a larger team. The goal of the project was to reduce the power consumption by an order of magnitude, compared to the nominal design.}
		\item{Performed Statistical Timing Analysis of critical paths in ultra low power consumption version of MSP 430, with Monte Carlo simulations of exported netlists in hspice.}
		\item{Determined deviations in behavior and identified potential problem points in design under new operating conditions.}
		\item{Developed framework to collate timing-critical paths under a known set of operating conditions, and simulate the same paths under various operating conditions to determine behavioral trends.}
		\end{cvitems}
	}

	\cventry
	{Intern}
	{EdZilla Software Technologies Pvt. Ltd.}
	{Bangalore, India}
	{May. 2012 - Jul. 2012}
	{
		\begin{cvitems}
		\item{Worked on tablet based educational product, supporting interactive learning for English and Mathematics in the vernacular medium. This product is deployed across rural public schools in Karnataka, India.}
		\item{Developed evaluation algorithm, and performance tracking and feedback system, helping each child learn at his/her own pace.}
		\end{cvitems}
	}

\end{cventries}
